Breast Cancer Diagnosis Classification Analysis

### 2022-12-09 powerpoint.rmd

```{r}
ggplot(train) +
  geom_point(aes(x = concavity_mean, y = radius_mean, col = diagnosis))+
  labs(x = "Concavity Mean", y = "Radius Mean", title = "Severity of Concavity vs. Radius of Tumor")
```

Different measurements of each variable are correlated

Relationship with Diagnosis visible for each measurement

@@

train$diagnosis <- as.factor(train$diagnosis)
test$diagnosis <- as.factor(test$diagnosis)
```

```{r}
ggplot(train) +
  geom_point(aes(x = concavity_mean, y = radius_mean, col = diagnosis))+
  labs(x = "Concavity Mean", y = "Radius Mean", title = "Severity of Concavity vs. Radius of Tumor")

train[,c(1,2,12,22)] |>
  ggpairs()
```

Different measurements of each variable are correlated

Relationship with Diagnosis visible for each measurement

@@

>>>>

@@

train$diagnosis <- as.factor(train$diagnosis)
test$diagnosis <- as.factor(test$diagnosis)

ggplot(train) +
  geom_point(aes(x = concavity_mean, y = radius_mean, col = diagnosis))+
  labs(x = "Concavity Mean", y = "Radius Mean", title = "Severity of Concavity vs. Radius of Tumor")
```

```{r}
train[,c(1,2,12,22)] |>
  ggpairs()
```

@@

# Preferred Models
